---
title: "Bayesian Evidence Synthesis"
author: "Thom Volker"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  ioslides_presentation:
    incremental: true
    logo: uu_logo.png
bibliography: "/Users/thomvolker/Documents/Master_Thesis/thesis_literature.bib"
csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Replication {.build}

Repetition increases the perceived truth equally for plausible and implausible statements [@fazio_presentation_2019].

<div class="centered">
```{r, message = F, warning = F, fig.height = 3}
library(purrr)
library(meta)

set.seed(1996)

nstudies <- 6

studies <- map(1:nstudies, ~rnorm(10, -1, 3))

meta_data2 <- list(n = sapply(studies, function(x) length(x)),
                   means = sapply(studies, mean),
                   sds = sapply(studies, sd))


metamean(n = meta_data2$n,
         mean = meta_data2$mean,
         sd = meta_data2$sds) %>% forest(comb.fixed = T,
                                         comb.random = F,
                                         overall = T,
                                         overall.hetstat = F)

```

</div>

Replication is nice, but not enough.

## Conceptual replications

- If a study is methodologically flawed, all direct replications will inherently exploit the flaws.

- Conceptual replications try to address a single problem from different angles. <!-- And thus inherently use different methodologies --> 
  * Different methodologies
  * Different operationalizations

- But how should we combine multiple studies with varying designs?

## Bayesian Evidence Synthesis

<!-- Meta analysis and sequantial updating are not applicable, so we need something else, which is available in the form of Bayesian Evidence Synthesis -->

Instead of addressing the parameter estimates, Bayesian Evidence Synthesis expresses the support for a given hypothesis in terms of a Bayes Factor [@kuiper_combining_2013].

1. Construct study-specific hypotheses that incorporate the models and operationalizations at hand.

2. Express the support for the study specific hypotheses in terms of a Bayes Factor. 

3. Combine the study-specific Bayes Factors by means of multiplication into one overall measure of evidence.

## Proposal {.build}

In general conditions, Bayesian Evidence Synthesis proved to work.

However, study-specific Bayes Factors depend on the fit and the complexity.

- How to handle hypotheses with varying dimensions?

- Can we incorporate underpowered studies?

- Optional: How to handle situations in which the sample sizes differ dramatically over the studies?

## Specifically {.build}

Simulations with multiple statistical models (e.g., linear, logit, probit and/or Poisson regression).

Vary:

- Sample sizes

- Number of parameters in the hypotheses

- Effect sizes

- Equality / inequality constrained hypotheses

Evaluate:

- True hypothesis rate

# Questions / comments / tips?

## References
